---
title: "Final Report: Test of `r params$test_article` Using `r params$assay_name`"
author: "`r params$author`"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true
  word_document: 
    toc: true
  pdf_document: 
    toc: true
editor_options: 
  markdown: 
    wrap: 72
params:
  test_article: "Hygenix Mask"
  assay_name: "MEM Elution"
  author: "Dr. John Doe"
  report_number: "HYX-M202309045(A)"
  glp_regulation: "21 CFR Part 58, U.S. FDA"
  protocol_inspection_date: "2024-09-10"
  procedure_inspection_date: "2024-09-12"
  raw_data_inspection_date: "2024-09-20"
  final_report_inspection_date: "2024-09-21"
  client_name: "Hygenix Inc."
  client_address: "300 Main Street, Springfield, USA"
  facility_name: "BioTech Labs"
  facility_address: "123 Research Ave, BioCity, USA"
  facility_website: "www.biotechlabs.com"
  facility_contact: "contact@biotechlabs.com, +1-800-555-1234"
  batch_number: "HYX-202305001"
  physical_state: "Solid"
  color: "Blue"
  size: "180 x 95 mm"
  storage_conditions: "Room temperature"
  intended_use: "To provide respiratory protection in medical settings by filtering particulate matter."
  negative_control_name: "Polyethylene Pellets"
  negative_control_color: "White"
  negative_control_physical_state: "Solid"
  negative_control_extraction_ratio: "3 cm²/mL"
  positive_control_name: "PVC Plastic"
  positive_control_color: "Clear"
  positive_control_physical_state: "Solid"
  positive_control_extraction_ratio: "3 cm²/mL"
  media_control: "MEM medium with 10% FBS"
  cell_line_name: "HeLa Cells"
  cell_line_source: "ATCC (American Type Culture Collection), USA"
  extraction_solvent: "MEM medium with 10% fetal bovine serum (FBS)"
  extraction_temp: "37°C"
  extraction_time: "72 hours"
  surface_area_volume_ratio: "3 cm²/mL"
  exposure_duration: "48 hours"
  concentration_levels: c("100%", "75%", "50%", "25%")
  endpoint: "Qualitative Scoring"
  deviation_statement: "No deviations from the approved study protocol were observed that would affect the validity of the data."
---

```{r, results="asis", echo=FALSE}
if (knitr::is_latex_output()) {
  cat("\\newpage")
} else if (knitr::is_html_output()) {
  cat('<div style="page-break-after: always;"></div>')
} else if (knitr::pandoc_to("docx")) {
  cat('<w:br />')
}
```

## 1. Report Information

**Report Number:** `r params$report_number`\
**Test Method:** `r params$assay_name`\
**Standard:** `r params$glp_regulation`\
**Sponsor:** `r params$client_name`\
**Address:** `r params$client_address`\
**Testing Facility:** `r params$facility_name`\
**Facility Address:** `r params$facility_address`\
**Website:** `r params$facility_website`\
**Contact Information:** `r params$facility_contact`

------------------------------------------------------------------------

```{r, results="asis", echo=FALSE}
if (knitr::is_latex_output()) {
  cat("\\newpage")
} else if (knitr::is_html_output()) {
  cat('<div style="page-break-after: always;"></div>')
} else if (knitr::pandoc_to("docx")) {
  cat('<w:br />')
}
```

## 2. Quality Assurance Statement

The Quality Assurance Unit inspected/audited this study in compliance
with the following GLP (Good Laboratory Practice) regulations:

-   **GLP Regulation:** `r params$glp_regulation`\
    The inspections were conducted on the following dates, and the
    findings were reported to the Study Director and Testing Facility
    Management:

-   **Study Protocol Inspection Date:**
    `r params$protocol_inspection_date`\

-   **Study Procedure Inspection Date:**
    `r params$procedure_inspection_date`\

-   **Raw Data Inspection Date:** `r params$raw_data_inspection_date`\

-   **Final Report Inspection Date:**
    `r params$final_report_inspection_date`

The final report accurately describes the test methods, and the results
are consistent with the raw data.

------------------------------------------------------------------------

```{r, results="asis", echo=FALSE}
if (knitr::is_latex_output()) {
  cat("\\newpage")
} else if (knitr::is_html_output()) {
  cat('<div style="page-break-after: always;"></div>')
} else if (knitr::pandoc_to("docx")) {
  cat('<w:br />')
}
```

## 3. Test and Control Articles

### 3.1 Test Article

-   **Name:** `r params$test_article`\
-   **Manufacturer:** `r params$client_name`\
-   **Batch/Lot Number:** `r params$batch_number`\
-   **Physical State:** `r params$physical_state`\
-   **Color:** `r params$color`\
-   **Size:** `r params$size`\
-   **Storage Conditions:** `r params$storage_conditions`\
-   **Intended Use:** `r params$intended_use`

### 3.2 Negative Control Article

-   **Name:** `r params$negative_control_name`\
-   **Extraction Ratio:** `r params$negative_control_extraction_ratio`\
-   **Physical State:** `r params$negative_control_physical_state`\
-   **Color:** `r params$negative_control_color`\
-   **Storage Conditions:** Room temperature\
-   **Extraction Solvent:** MEM medium with 10% fetal bovine serum
    (FBS).

### 3.3 Positive Control Article

-   **Name:** `r params$positive_control_name`\
-   **Extraction Ratio:** `r params$positive_control_extraction_ratio`\
-   **Physical State:** `r params$positive_control_physical_state`\
-   **Color:** `r params$positive_control_color`\
-   **Extraction Solvent:** MEM medium with 10% FBS.

### 3.4 Media Control

-   **Name:** `r params$media_control`

------------------------------------------------------------------------

## 4. Pre and Post Extract Appearance

-   **Pre-Extract Appearance:** Clear and free of particulates.\
-   **Post-Extract Appearance:** No significant color changes were noted
    for both the test article and controls.

------------------------------------------------------------------------

## 5. Test System

### 5.1 Cell Line

-   **Name:** `r params$cell_line_name`, obtained from
    `r params$cell_line_source`.\
-   **Justification:** `r params$cell_line_name` cells are widely used
    for cytotoxicity studies due to their sensitivity to cytotoxic
    extracts.

------------------------------------------------------------------------

## 6. Experimental Design

### 6.1 Preparation of Extracts

-   **Extraction Solvent:** `r params$extraction_solvent`.\
-   **Extraction Conditions:**
    -   The test article was extracted at a surface area-to-volume ratio
        of `r params$surface_area_volume_ratio` at
        `r params$extraction_temp` for `r params$extraction_time`.

### 6.2 Procedure

-   Following extraction, the cells were exposed to the test article
    extract, as well as the positive and negative control extracts, and
    the media control for `r params$exposure_duration`.\
-   The test article extract was prepared at concentrations of
    `r paste(params$concentration_levels, collapse = ", ")`.\
-   The cells were incubated for 24 hours, after which cytotoxicity was
    assessed by the percentage of cell viability using the MTT assay.\
-   Cell morphology was observed to evaluate any changes that could
    indicate cytotoxicity.

------------------------------------------------------------------------

```{r, results="asis", echo=FALSE}
if (knitr::is_latex_output()) {
  cat("\\newpage")
} else if (knitr::is_html_output()) {
  cat('<div style="page-break-after: always;"></div>')
} else if (knitr::pandoc_to("docx")) {
  cat('<w:br />')
}
```

## 7. Results

### 7.1 Acceptance Criteria

| Grade        | Criteria                                                                              |
|-------------------|-----------------------------------------------------|
| 0 - None     | No cell lysis observed; intracytoplasmic granules present.                            |
| 1 - Slight   | Less than or equal to 20% rounding of cells with occasional lysed cells.              |
| 2 - Mild     | Greater than 20% to less than or equal to 50% rounding, with no extensive cell lysis. |
| 3 - Moderate | Greater than 50% rounding with lysed cells.                                           |
| 4 - Severe   | Nearly complete destruction of the cell layers.                                       |

The mean reactivity score of the three replicates will be reported using
`r params$endpoint`.

------------------------------------------------------------------------

## 9. Record Storage

All raw data and a copy of the final report will be retained in the
designated archive.

------------------------------------------------------------------------

## 10. Confidentiality Agreement

All confidentiality statements were agreed upon before the initiation of
the study.

------------------------------------------------------------------------

## 12. Deviation Statement

`r params$deviation_statement`

------------------------------------------------------------------------
