---
title: "ISO 10993-5 MEM Elution Test Report"
author: "Jeffey Plume"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
fontsize: 12pt
geometry: margin=1in
subtitle: "Assessment of `r params$test_article`"
abstract: |  
  This report summarizes the results of the MEM Elution assay for the cytotoxicity testing of `r params$test_article`. The purpose of this test is to assess the cytotoxic potential of the test article to determine if the material exhibits any toxic effects on mammalian cells.
header-includes: 
  - \usepackage{graphicx}
  - \usepackage{booktabs}
  - \usepackage{float}
  - \usepackage{amsmath}
  - \usepackage{fancyhdr}
  - \usepackage{lastpage}
  - \usepackage{hyperref}
  - \newpage              # Force a page break before TOC
  - \hypersetup{colorlinks=true, linkcolor=blue, filecolor=magenta, urlcolor=cyan}
  - \urlstyle{same}
  - \pagestyle{fancy}
  - \fancyhead[L]{ISO 10993-5 Cytotoxicity Test Report}
  - \fancyhead[R]{ACME Labs Inc.}
  - \fancyfoot[C]{Page \thepage\ of \pageref{LastPage}}
output: 
  word_document: 
    toc: true
    reference_docx: "latex_template.dotx"
  html_document: 
    toc: true
  pdf_document: 
    toc: true
    keep_md: true
    latex_engine: xelatex
editor_options: 
  markdown: 
    wrap: 72
params:
  report_number: "ACME-001"
  sample_received_date: "2024-09-01"
  protocol_inspection_date: "2024-09-07"
  experiment_start_date: "2024-09-08"
  procedure_inspection_date: "2024-09-11"
  experiment_end_date: "2024-09-13"
  raw_data_inspection_date: "2024-09-14"
  final_report_inspection_date: "2024-09-15"
  quality_manager: "Mr. Bugs Bunny"
  study_director: "Wile E. Coyote"
  pre_extraction_observations: "All extracts were clear and free of particulates prior to the extraction process."
  post_test_article: "No significant color changes were observed, and the extract remained clear."
  post_negative_control: "No significant color changes were observed, and the extract remained clear."
  post_positive_control: "The extract became cloudy, and filtration was required before use."
  ph_adjustment: "No pH adjustments, centrifugation, or dilution processes were performed on the test and control samples."
  test_article: "Dehydrated Boulders"
  manufacturer: "ACME Corporation"
  batch_number: "BB1940WSC"
  expiration: "2025-12-31"
  physical_state: "Solid"
  color: "White"
  size: "100 x 100 mm"
  storage_conditions: "Room temperature"
  intended_use: "To expand into boulders with the addition of water."
  extraction_duration: "72 hours"
  extraction_ratio: "3 cm³:1 mL"
  test_actual_volume: "166.25 cm³"
  test_extract_volume: "64.9 mL"
  lot_fbs: "FBS-LOT-2024"
  exp_fbs: "2025-01-31"
  lot_mem: "MEM-LOT-5678"
  exp_mem: "2025-06-30"
  lot_trypsin: "TRYPSIN-LOT-9012"
  exp_trypsin: "2025-08-15"
  lot_penstrep: "PENSTREP-LOT-3456"
  exp_penstrep: "2025-11-01"
  lot_pbs: "PBS-LOT-7890"
  exp_pbs: "2026-01-20"
  lot_isopropanol: "ISO-LOT-1122"
  exp_isopropanol: "2026-03-15"
  test_extract_appearance: "Clear"
  positive_extract_appearance: "Cloudy"
  negative_extract_appearance: "Clear"
  blank_extract_appearance: "Clear"
  lot_number_positive_control: "LATEX-LOT-1234"
  positive_control_expiration: "2025-06-30"
  lot_number_negative_control: "POLY-LOT-5678"
  negative_control_expiration: "2025-03-15"
  score_replicate1: "0 (None)"
  score_replicate2: "0 (None)"
  score_replicate3: "0 (None)"
  score_positive_replicate1: "4 (Severe)"
  score_positive_replicate2: "4 (Severe)"
  score_positive_replicate3: "4 (Severe)"
  score_negative_replicate1: "0 (None)"
  score_negative_replicate2: "0 (None)"
  score_negative_replicate3: "0 (None)"
  score_blank_replicate1: "0 (None)"
  score_blank_replicate2: "0 (None)"
  score_blank_replicate3: "0 (None)"
---

```{r, results="asis", echo=FALSE}
if (knitr::is_latex_output()) {
  cat("\\newpage")
} else if (knitr::is_html_output()) {
  cat('<div style="page-break-after: always;"></div>')
} else {
  cat("\\pagebreak ")
}
```

## Quality Assurance Statement

The Quality Assurance Unit inspected/audited this study in compliance
with the following regulations:

<br>

**Good Laboratory Practice for Nonclinical Laboratory Studies, Title 21
of the Code of Federal Regulations, Part 58 (21 CFR Part 58)**

## Inspections Overview

The Quality Assurance Unit conducted inspections on the following dates.
The findings were reported to the Study Director. The final report was
reviewed by the Quality Assurance Unit. The final report accurately
describes the test methods in accordance with standard operating
procedures, and the results are consistent with raw data from
non-clinical studies conducted according to the study protocol.

<br>

| Inspection      | Date of Inspection                      | Performed by               | Date Reported to Study Director         |
|------------------|------------------|------------------|-------------------|
| Study Protocol  | `r params$protocol_inspection_date`     | `r params$quality_manager` | `r params$protocol_inspection_date`     |
| Study Procedure | `r params$procedure_inspection_date`    | `r params$quality_manager` | `r params$protocol_inspection_date`     |
| Raw Data        | `r params$raw_data_inspection_date`     | `r params$quality_manager` | `r params$raw_data_inspection_date`     |
| Final Report    | `r params$final_report_inspection_date` | `r params$quality_manager` | `r params$final_report_inspection_date` |

```{r, results='asis', echo=FALSE}
if (knitr::is_html_output()) {
  cat('
  <table style="border-collapse: collapse; border: none; width: 100%;">
    <tr>
      <td style="border: none; width: 50%;"></td>
      <td style="border: none; width: 50%;"></td>
    </tr>
    <tr>
      <td style="border: none; height: 40px;">&nbsp;</td> <!-- Extra space above the signature lines -->
      <td style="border: none; height: 40px;">&nbsp;</td> <!-- Adjust this height as necessary -->
    </tr>
    <tr>
      <td style="border: none; width: 50%;">______________________</td>
      <td style="border: none; width: 50%;">______________________</td>
    </tr>
    <tr>
      <td style="border: none;">', params$quality_manager, '</td>
      <td style="border: none;">Date</td>
    </tr>
    <tr>
      <td style="border: none;">Quality Manager</td>
      <td style="border: none;"></td>
    </tr>
    <tr>
      <td style="border: none; height: 40px;">&nbsp;</td> <!-- Extra space for Study Director signature -->
      <td style="border: none; height: 40px;">&nbsp;</td>
    </tr>
    <tr>
      <td style="border: none; width: 50%;">______________________</td>
      <td style="border: none; width: 50%;">______________________</td>
    </tr>
    <tr>
      <td style="border: none;">Study Director</td>
      <td style="border: none;">Date</td>
    </tr>
  </table>
  ')
} else if (knitr::is_latex_output()) {
  quality_manager <- params$quality_manager
  study_director <- params$study_director
  cat('
  \\begin{tabular}{p{6cm} p{6cm}}
  \\\\[10mm]
  \\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_ & \\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_ \\\\
  ', quality_manager, ' & Date \\\\
  Quality Manager &  \\\\[10mm]
  \\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_ & \\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_ \\\\
  ', study_director, ' & Date \\\\
  Study Director &  \\\\
  \\end{tabular}
  ')
} else {
  cat('
  |                            |                          |
  |----------------------------|--------------------------|
  |                            |                          | 
  | ______________________     | ______________________    |
  | ', params$quality_manager, ' | Date                     |
  | Quality Manager            |                          |
  |                            |                          | 
  | ______________________     | ______________________    |
  | ', params$study_director, '  | Date                     |
  | Study Director             |                          |
  ')
}

```

```{r, results="asis", echo=FALSE}
if (knitr::is_latex_output()) {
  cat("\\newpage")
} else if (knitr::is_html_output()) {
  cat('<div style="page-break-after: always;"></div>')
} else {
  cat("\\pagebreak ")
}
```

## GLP Compliance Statement

This study was fully in accordance with the technical requirements of
the study protocol.

This study was conducted in compliance with Good Laboratory Practice
(GLP) Regulation 21 CFR Part 58, U.S. Food and Drug Administration
(FDA).

|                              |                                         |
|------------------------------|----------------------------------------:|
| Test Article Receipt         |         `r params$sample_received_date` |
| Protocol Effective Date      |     `r params$protocol_inspection_date` |
| Technical Initiation Date    |        `r params$experiment_start_date` |
| Technical Completion Date    |          `r params$experiment_end_date` |
| Final Report Completion Date | `r params$final_report_inspection_date` |

```{r, results='asis', echo=FALSE}
if (knitr::is_html_output()) {
  cat('
  <table style="border-collapse: collapse; border: none; width: 100%;">
    <tr>
      <td style="border: none; width: 50%;"></td>
      <td style="border: none; width: 50%;"></td>
    </tr>
    <tr>
      <td style="border: none; height: 40px;">&nbsp;</td> <!-- Extra space above the signature lines -->
      <td style="border: none; height: 40px;">&nbsp;</td> <!-- Adjust this height as necessary -->
    </tr>
    <tr>
      <td style="border: none; width: 50%;">______________________</td>
      <td style="border: none; width: 50%;">______________________</td>
    </tr>
    <tr>
      <td style="border: none;">', params$quality_manager, '</td>
      <td style="border: none;">Date</td>
    </tr>
    <tr>
      <td style="border: none;">Quality Manager</td>
      <td style="border: none;"></td>
    </tr>
    <tr>
      <td style="border: none; height: 40px;">&nbsp;</td> <!-- Extra space for Study Director signature -->
      <td style="border: none; height: 40px;">&nbsp;</td>
    </tr>
    <tr>
      <td style="border: none; width: 50%;">______________________</td>
      <td style="border: none; width: 50%;">______________________</td>
    </tr>
    <tr>
      <td style="border: none;">Study Director</td>
      <td style="border: none;">Date</td>
    </tr>
  </table>
  ')
} else if (knitr::is_latex_output()) {
  quality_manager <- params$quality_manager
  study_director <- params$study_director
  cat('
  \\begin{tabular}{p{6cm} p{6cm}}
  \\\\[10mm]
  \\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_ & \\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_ \\\\
  ', quality_manager, ' & Date \\\\
  Quality Manager &  \\\\[10mm] % Adds 10mm vertical space before the signature
  % Adding a second signature line for Study Director
  \\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_ & \\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_\\_ \\\\
  ', study_director, ' & Date \\\\
  Study Director &  \\\\
  \\end{tabular}
  ')
} else {
  cat('
  |                            |                          |
  |----------------------------|--------------------------|
  |                            |                          | <!-- Empty line for vertical space -->
  | ______________________     | ______________________    |
  | ', params$quality_manager, ' | Date                     |
  | Quality Manager            |                          |
  |                            |                          | <!-- Empty line for vertical space -->
  | ______________________     | ______________________    |
  | ', params$study_director, '  | Date                     |
  | Study Director             |                          |
  ')
}

```

```{r, results="asis", echo=FALSE}
if (knitr::is_latex_output()) {
  cat("\\newpage")
} else if (knitr::is_html_output()) {
  cat('<div style="page-break-after: always;"></div>')
} else {
  cat("\\pagebreak ")
}
```
```

## Summary

### Test and Control Articles

| **Article Type** | **Name**                | **Lot Number**                         | **Expiration**                         | **Storage**                   |
|---------------|---------------|---------------|---------------|---------------|
| Test Article     | `r params$test_article` | `r params$batch_number`                | `r params$expiration`                  | `r params$storage_conditions` |
| Negative Control | Polyethylene Pellets    | `r params$lot_number_negative_control` | `r params$negative_control_expiration` | Room temperature              |
| Positive Control | Latex                   | `r params$lot_number_positive_control` | `r params$positive_control_expiration` | Room temperature              |
| Blank Control    | N/A                     | —                                      | N/A                                    | Room temperature              |

### Test Method

Potential toxicity of test article was evaluated using the MEM Elution
method in accordance with ISO 10993-5: 2009 Biological evaluation of
Medical Devices—Part 5: Tests for in vitro Cytotoxicity. Study protocol
number: ACME-CYTO

### Conclusion

Under the conditions of this study, the test article extract did not
show cytotoxic potential when testing on L929 cells.

```{r, results="asis", echo=FALSE}
if (knitr::is_latex_output()) {
  cat("\\newpage")
} else if (knitr::is_html_output()) {
  cat('<div style="page-break-after: always;"></div>')
} else {
  cat("\\pagebreak ")
}
```

## Purpose

The purpose of this test was to determine the biological reactivity of
mouse fibroblast L929 cells in response to the test
article—`r params$test_article`. This study evaluated whether the test
article exhibited any toxic effects on mammalian cells under in vitro
conditions. Specifically, the test assessed the cytotoxic potential to
determine the safety and biocompatibility of the material when used
according to its intended purpose.

## Regulatory Standards

This study was conducted in accordance with the following regulatory
standards:
<br>
1.  **ISO 10993-1**: *Evaluation and Testing within a Risk Management
    Process*—General requirements for evaluating the biological impact
    of medical devices.
2.  **ISO 10993-5:2009**: *Biological Evaluation of Medical Devices—Part
    5: Tests for in vitro Cytotoxicity*—Provides guidelines for
    evaluating the potential cytotoxic effects of a medical device
    material on cells.
3.  **ISO 10993-12**: *Sample Preparation and Reference
    Materials*—Guidelines for preparing samples and reference materials
    for testing to ensure consistent and reliable results.
<br>
These standards ensure that the study was conducted with the highest
level of scientific rigor and consistency, providing a reliable
assessment of the biological impact of the test article.

## Compliance

This study complies with the following regulations:
<br>
1.  **Good Laboratory Practice (GLP) Regulations (21 CFR Part 58)**: GLP
    standards ensure that the study is conducted with transparency,
    accountability, and rigorous scientific practices, guaranteeing the
    integrity of the study data.\

2.  **ISO/IEC 17025:2017**: *General Requirements for the Competence of
    Testing and Calibration Laboratories*—ISO 17025 accreditation
    ensures that the testing facility is competent to perform laboratory
    testing with a high degree of accuracy and reliability.
<br>
Compliance with these regulations guarantees that the study data meets
both legal and quality assurance requirements, ensuring the validity and
credibility of the test results.

```{r, results="asis", echo=FALSE}
if (knitr::is_latex_output()) {
  cat("\\newpage")
} else if (knitr::is_html_output()) {
  cat('<div style="page-break-after: always;"></div>')
} else {
  cat("\\pagebreak ")
}
```

## Test and Control Articles

### Test Article

|                        |                               |
|------------------------|-------------------------------|
| **Name**               | `r params$test_article`       |
| **Manufacturer**       | `r params$manufacturer`       |
| **Batch/Lot Number**   | `r params$batch_number`       |
| **Expiration Date**    | `r params$expiration`         |
| **Storage Conditions** | `r params$storage_conditions` |

\*Note\*\* The information about the test article was supplied by the
sponsor wherever applicable. The Sponsor is responsible for all test
article characterization data as specified in the GLP.

### Negative Control Article

|                        |                                              |
|------------------------|----------------------------------------------|
| **Name**               | High-density Polyethylene (HDPE)             |
| **Extraction Ratio**   | 3 cm²/1 mL                                   |
| **Physical State**     | Solid                                        |
| **Color**              | White                                        |
| **Storage Conditions** | Room temperature                             |
| **Extraction Solvent** | MEM medium with 10% fetal bovine serum (FBS) |

### Positive Control Article

|                        |                         |
|------------------------|-------------------------|
| **Name**               | Latex                   |
| **Extraction Ratio**   | 3 cm²/1 mL              |
| **Physical State**     | Solid                   |
| **Color**              | Tan                     |
| **Storage Conditions** | Room temperature        |
| **Extraction Solvent** | MEM medium with 10% FBS |

### Media Control

MEM medium with 10% fetal bovine serum (FBS)

```{r, results="asis", echo=FALSE}
if (knitr::is_latex_output()) {
  cat("\\newpage")
} else if (knitr::is_html_output()) {
  cat('<div style="page-break-after: always;"></div>')
} else {
  cat("\\pagebreak ")
}
```

## Equipment and Reagents

### Equipment

| **Equipment Name**  | **Equipment Number** | **Calibration Expire** |
|---------------------|----------------------|------------------------|
| Autoclave           | ACME-001             | 2025-03-09             |
| CO2 Incubator       | BUGS-006             | 2025-03-09             |
| Inverted microscope | DAFFY-007            | 2025-06-15             |

### Reagents

| **Reagent Name**                | **Manufacturer**           | **Part Number** | **Lot Number**             | **Expiration Date**        |
|-------------------|--------------|--------------|--------------|--------------|
| Fetal Bovine Serum (FBS)        | Wile E. Biotech Industries | FBS-002         | `r params$lot_fbs`         | `r params$exp_fbs`         |
| MEM Medium                      | Road Runner Labs           | MEM-003         | `r params$lot_mem`         | `r params$exp_mem`         |
| Trypsin                         | Bugs Bunny Pharmaceuticals | TRYPSIN-004     | `r params$lot_trypsin`     | `r params$exp_trypsin`     |
| Penicillin/Streptomycin         | Daffy Duck Labs            | PENSTREP-005    | `r params$lot_penstrep`    | `r params$exp_penstrep`    |
| PBS (Phosphate-buffered saline) | Tweety Solutions           | PBS-006         | `r params$lot_pbs`         | `r params$exp_pbs`         |
| Isopropanol (99.9%)             | ACME Industrial Reagents   | ISO-007         | `r params$lot_isopropanol` | `r params$exp_isopropanol` |

## Identification of Test System

L929 mouse fibroblast cells obtained from ATCC (American Type Culture
Collection), USA.

## Justification of Test System and Route of Administration

Historically, mouse fibroblast L929 cells have been used for
cytotoxicity studies because they demonstrate sensitivity to extractable
cytotoxic articles. The test article was extracted and administered in
vitro to mouse fibroblast L929 cells through a solvent compatible with
the test system. This was the optimal route of administration available
in this test system as recommended in the guidelines.

```{r, results="asis", echo=FALSE}
if (knitr::is_latex_output()) {
  cat("\\newpage")
} else if (knitr::is_html_output()) {
  cat('<div style="page-break-after: always;"></div>')
} else {
  cat("\\pagebreak ")
}
```

## Experimental Design

### Extraction Process

The extraction process was carried out at an extraction ratio of
**`r params$extraction_ratio`** for all samples. Under aseptic
conditions, samples were extracted with continuous agitation in closed,
inert containers, using **DMEM medium with 10% fetal bovine serum
(FBS)** as the extraction solvent.
<br>
| **Sample**       | **Extract Volume (mL)**        | **Appearance of Extract**              |
|--------------------|-------------------------|---------------------------|
| Test Article     | `r params$test_extract_volume` | `r params$test_extract_appearance`     |
| Negative Control | `r params$test_extract_volume` | `r params$negative_extract_appearance` |
| Positive Control | `r params$test_extract_volume` | `r params$positive_extract_appearance` |
| Blank Control    | `r params$test_extract_volume` | `r params$blank_extract_appearance`    |

## Experimental Procedure

Once the extracts were prepared, they were tested on **L929 mouse
fibroblast cells** using a standard cytotoxicity assay. The cells were
cultured in a 96-well plate and exposed to the test article extract and
controls for approximately 48 hours.

### Evaluation Criteria

Morphological assessment of cytotoxicity was based on the following grading system:

<br>

| **Grade**        | **Criteria**                                                                     |
|---------------------|---------------------------------------------------|
| **0 - None**     | No cell lysis observed; cells remained attached, with intracytoplasmic granules. |
| **1 - Slight**   | ≤ 20% rounding of cells, with occasional lysed cells observed.                   |
| **2 - Mild**     | \> 20% to ≤ 50% rounding, with no extensive cell lysis.                          |
| **3 - Moderate** | \> 50% rounding, with lysed cells present.                                       |
| **4 - Severe**   | Nearly complete destruction of the cell layer, with extensive lysis.             |

### Statistical Method

The mode of three replicates will be calculated to evaluate cytotoxic
potential.

```{r, results="asis", echo=FALSE}
if (knitr::is_latex_output()) {
  cat("\\newpage")
} else if (knitr::is_html_output()) {
  cat('<div style="page-break-after: always;"></div>')
} else {
  cat("\\pagebreak ")
}
```

## Results

### Pre-Extraction Observations

| **Observation** | **Details**                            |
|-----------------|----------------------------------------|
| Pre-Extraction  | `r params$pre_extraction_observations` |

### Post-Extraction Observations

| **Sample**       | **Post-Extraction Observation**  |
|------------------|----------------------------------|
| Test Article     | `r params$post_test_article`     |
| Negative Control | `r params$post_negative_control` |
| Positive Control | `r params$post_positive_control` |

**General Observations**

`r params$ph_adjustment`

**Post-Extraction Observation**

-   **Test Article**: No significant color changes were observed, and
    the extract remained clear.
-   **Negative Control**: No significant color changes were observed,
    and the extract remained clear.
-   **Positive Control**: The extract became cloudy, and filtration was
    required before use.

No pH adjustments, centrifugation, or dilution processes were performed
on the test and control samples.

### Morphological Scoring

Each sample was tested in triplicate. The table below shows the results
of the qualitative assessment of cytotoxicity:

<br>

| **Sample**       | **Replicate 1**                      | **Replicate 2**                      | **Replicate 3**                      | **Modal Score**                      |
|---------------|---------------|---------------|---------------|---------------|
| Test Article     | `r params$score_replicate1`          | `r params$score_replicate2`          | `r params$score_replicate3`          | `r params$score_replicate1`          |
| Positive Control | `r params$score_positive_replicate1` | `r params$score_positive_replicate2` | `r params$score_positive_replicate3` | `r params$score_positive_replicate1` |
| Negative Control | `r params$score_negative_replicate1` | `r params$score_negative_replicate2` | `r params$score_negative_replicate3` | `r params$score_negative_replicate1` |
| Blank Control    | `r params$score_blank_replicate1`    | `r params$score_blank_replicate2`    | `r params$score_blank_replicate3`    | `r params$score_blank_replicate1`    |

## Conclusion

The **test article extract**, when tested in triplicate, did not exhibit
any cytotoxic effects at the tested concentration, as indicated by the
**modal reactivity score** of **0 (None)**. The positive control
demonstrated expected **severe cytotoxicity**, while the negative and
blank controls showed **no cytotoxicity**.

## Record Storage

All raw data generated during this study, along with a copy of the final
report, have been securely archived at **ACME Labs**' designated storage
facility in accordance with internal protocols and regulatory
requirements.

## Confidentiality Agreement

The confidentiality of all data and study-related materials has been
maintained as per the confidentiality agreement established prior to the
initiation of the study.

## Deviation Statement

There were no deviations from the approved study protocol that would
impact the validity or integrity of the data.
